Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-08-28 analysis/presentation/sim_survey_presentation.Rmd
Add a plot for describing the spatial simulation to the presentation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.height = 4.5, 
                      fig.width = 10)
knitr::opts_knit$set(root.dir = "../..")
```

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")

@@

@@

Trend in total abundance

<dev class = "centered"> 
<!-- There is a bug somewhere...had to contain plotly plots in a dev to get it working -->
```{r}
plot_trend(sim) %>% 
  layout(plot_bgcolor = "transparent",
         paper_bgcolor = "transparent",
         margin = list(l = 70, r = 0, t = 0, b = 40, pad = 0),
         font = list(size = 14))
```
</dev>

Trend in abundance at age

<dev class = "centered">
```{r}
plot_surface(sim) %>% 
  layout(plot_bgcolor = "transparent",
         paper_bgcolor = "transparent",
         margin = list(l = 0, r = 0, t = 0, b = 0, pad = 0),
         font = list(size = 14))
```
</dev>

@@

@@

- Try and figure out the bug that prevents the plotly plots from working in this part of the slideshow (alternate fix to containing it in a device)
- Figure out how to use the Google Font with plotly
- Set-up global layout arguents somehow

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.width = 10, 
                      fig.height = 5)
knitr::opts_knit$set(root.dir = "../..")
```

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(crosstalk)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")

@@

## wrapper for layout with some different defaults for this slideshow
tight_layout <- function(p, 
                         plot_bgcolor = "transparent",
                         paper_bgcolor = "transparent",
                         margin = list(l = 0, r = 0, t = 0, b = 0, pad = 0),
                         font = list(size = 14), ..., data = NULL) {
  layout(p, plot_bgcolor = plot_bgcolor, paper_bgcolor = paper_bgcolor,
         margin = margin, font = font, ..., data = data)
}

@@

## Simulate abundance {.tighter}

### Trend in total abundance

<dev class = "left">
<!-- There is a bug somewhere...had to contain plotly plots in a dev to get it working -->
```{r}
plot_trend(sim) %>% 
  tight_layout(margin = list(l = 70, r = 0, t = 0, b = 40, pad = 0))
```
</dev>

## Simulate abundance {.tighter}

### Trend in abundance at age

<dev class = "left">
```{r}
plot_surface(sim) %>% tight_layout()
```
</dev>

@@

## Simulate spatial aggregation  {.tighter}

### Square grid with depth gradient

<dev class = "left">
```{r}
plot_ly(data = sim$grid_xy, x = ~x, y = ~y, z = ~depth, type = "heatmap") %>%
  colorbar(title = "Depth") %>%
  tight_layout(yaxis = list(title = "", scaleanchor = "x", zeroline = FALSE, 
                            showgrid = FALSE, showticklabels = FALSE,
                            tickcolor = "transparent"),
               xaxis = list(title = "", zeroline = FALSE, 
                            showgrid = FALSE, showticklabels = FALSE,
                            tickcolor = "transparent"))
```
</dev>

## Simulate spatial aggregation {.tighter}

### Distribution for ages 1-6 in years 1-6

<dev class = "left">
```{r}
plot_distribution_slider(sim, ages = 1:6, years = 1:6) %>% 
  tight_layout(margin = list(l = 0, r = 0, t = 40, b = 0, pad = 0))
```
</dev>

@@

- Try and figure out the bug that prevents the plotly plots from working in this part of the slideshow (alternate fix to containing it in a device)
- Figure out how to use the Google Font with plotly
- Set-up global layout arguents somehow
- Figure out how to make a sub-title for a slide below main title
- Reverse color ramp in grid figure
- Frame by year for spatial abundance plot (consider fixing one year, animate age / fix age and animate year)
